\bf Estimating the number of clusters using cross-validation

### 2019-01-11 JCGS-R2/response/response.tex

\item \textit{Bottom of page 4. The authors need to clarify the notation}

\textbf{Response:} \todo

%The fold numbers r and r_i are not well-defined. Please maintain the
%notational consistency. You defined only "r_i". What do you mean by: 'For each
%"fold" r'?

\item \textit{Page 6. Clarify that $N \geq K$, $M \geq K$.}

Added the sentence: ``For this cross-validation to be possible, we must have that
$K \leq N$ and $L \leq M$.''

@@

Added the sentence: ``For this cross-validation to be possible, we must have that
$K \leq N$ and $L \leq M$.''

%By my understanding, the authors must assume further that
%
%n  >> K
%m >> K	
%
%That is, they need to ensure that they are choosing n and m larger that K.
%This limitation should be clarified to the reader.

\item \textit{Section 2.2. Clarify the context in which the method is applied.}

Changed the first sentence as follows: ``Our version of Gabriel
cross-validation for clustering works is designed to find the best number of
clusters to use for $N$~observations of a $P$-dimensional random variable with
real-valued components.''

### 2019-01-11 JCGS-R2/cvclust.tex
Require K <= N

Our version of Gabriel cross-validation for clustering works by performing a
sequence of ``folds'' over the data. We use these folds to estimate a version
of prediction error (cross-validation error) for each possible value of $k$;
we then choose the value $\hat k$ with the smallest cross-validation error.

@@

To choose the folds, we randomly partition the rows and columns into $K$ and
$L$ subsets, respectively.  Each fold is indexed by a pair $(r,s)$ of
integers, with $r \in \{1, \dotsc, K\}$ and $s \in \{1, \dotsc, L\}$.  Fold
$(r,s)$ treats the $r$th row subset as ``test'', and the $s$th column subset
as ``response''.  We typically take $K = 5$ and $L = 2$.  For the number of
clusters, we select the value of $k$ that minimizes the average of $\CV(k)$
over all $K \times L$ folds (choosing the smallest value of $k$ in the event
of a tie).

>>>>

Our version of Gabriel cross-validation for clustering works is designed to
find the best number of clusters to use for $N$~observations of a
$P$-dimensional random variable with real-valued components.
The procedure works by performing a
sequence of ``folds'' over the data. We use these folds to estimate a version
of prediction error (cross-validation error) for each possible value of $k$;
we then choose the value $\hat k$ with the smallest cross-validation error.

@@

To choose the folds, we randomly partition the rows and columns into $K$ and
$L$ subsets, respectively.  Each fold is indexed by a pair $(r,s)$ of
integers, with $r \in \{1, \dotsc, K\}$ and $s \in \{1, \dotsc, L\}$.  Fold
$(r,s)$ treats the $r$th row subset as ``test'', and the $s$th column subset
as ``response''. 
For this cross-validation to be possible, we must have that
$K \leq N$ and $L \leq M$.
We typically take $K = 5$ and $L = 2$.  For the number of
clusters, we select the value of $k$ that minimizes the average of $\CV(k)$
over all $K \times L$ folds (choosing the smallest value of $k$ in the event
of a tie).
